% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX root = ../MasterThesis_OlivierChurlaud_2016.tex

\chapter{Conclusion}
\label{sec:conclusion}
\section{Master thesis summary}
To provide BESSY~II users a reliable light, the electrons' orbit in the storage ring must be finely controlled. To remove perturbations, a process based on multiple actors implements an inverse problem solving coupled with a PID corrector. After the process was modernized to be easily expandable, a dynamic correction was designed resulting in complete removal of the \SI{10}{\hertz} harmonic perturbation. The implementation of a simulation environment allowed for synthesizing and testing correctors. An improved PID and an optimal corrector were proposed to enhance the current correction process.

As some perturbations cannot or are difficult to correct, algorithms succeededin  localizing their source with a precision of around 1\% of the circumference if they affect orbit vertically, and around 10 to 20\% if it does horizontally.

As all the tools have been developed in a very modular way and precisely documented, they can hopefully be reused and expanded in the future by the accelerator department, which was supervising this thesis.

\section{Possible extension and future work}

The duration of the master thesis being limited, some interesting developments were only slightly considered and not deepened.

\begin{itemize}
    \item In this thesis, the system identification did not use any theoretical or physical input. To achieve better correction and control results, a more precise system analysis of the storage ring should be conducted, which would allow a more constrained and less noise sensitive identification.
    \item As the storage ring is a MIMO system (several corrector magnets, influencing the response of several BPMs) with coupling effect also between the horizontal and vertical axes, future work should go in the direction of synthesizing robust MIMO correctors.
    \item On the localization side, implementing an algorithm able to localize several perturbations seem to be a very challenging mathematical study.
\end{itemize}